---
title: "Presentation & Plotly"
author: "IsaacVillatoro"
date: "September 28, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Loading library and variables

```{r}
library(plotly)

x <- seq_len(nrow(volcano)) + 100
y <- seq_len(ncol(volcano)) + 500

```

## 3D plot

In scatter traces, we saw how to make 3D scatter plots and 3D paths/lines, but plotly.js also supports 3D surface and triangular mesh surfaces (aka trisurf plots).

```{r}
plot_ly() %>% add_surface(x = ~x, y = ~y, z = ~volcano)
```


*https://plotly-book.cpsievert.me/other-3d-plots.html*

*Figure: A 3D surface of volcano height.*