---
title: "Presentation & Plotly"
author: "IsaacVillatoro"
date: "September 28, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Loading library and variables

```{r, echo=TRUE}
library(plotly)
```

## Histogram

A histogram is an accurate graphical representation of the distribution of numerical data. It is an estimate of the probability distribution of a continuous variable (quantitative variable) and was first introduced by Karl Pearson. It is a kind of bar graph.

```{r echo=TRUE, eval=FALSE}
graph1=plot_ly(x = rnorm(700), type = "histogram")
graph1
```

*Reference: en.wikipedia.org/wiki/Histogram*

## Plot

```{r}
graph1=plot_ly(x = rnorm(700), type = "histogram")
graph1
```

